Overview

### 2019-03-15 notebooks/general_info.Rmd
framework for per-package tallies is available. will get top poly packages soon

>>>>

What are the counts now?
```{r}
total_mono_type_basic_no_null_real <- apply_count_to_lopkg_c(los_basic_no_null_real, args_count_all_mono_type)
total_mono_all_basic_no_null_real <- apply_count_to_lopkg_c(los_basic_no_null_real, args_count_all_mono_all)
```

Great.
Now, what are the top instances of type-based polymorphism?
```{r}
poly_type_args_basic_no_null_real <- reduce_extracted_lopkgs_to_one(apply_extract_to_lopkg(los_basic_no_null_real, extract_poly_type_args))
poly_type_args_basic_no_null_real <- poly_type_args_basic_no_null_real[order(-poly_type_args_basic_no_null_real$count),] # sort by count
poly_type_args_basic_no_null_real$perc <- round(poly_type_args_basic_no_null_real$count/sum(poly_type_args_basic_no_null_real$count) * 100, 2)
```

What's the top?
```{r}
format_df_for_print(poly_type_args_basic_no_null_real[1:20,])
```

Ok.
What if we want some per package information?
Well, to do it on one package (let's try rlang):

```{r}
rlang_tally <- tally_up_lofun_c(los$rlang)
rlang_tally$tot_args
rlang_tally$tot_mono_args_type
format_df_for_print(rlang_tally$top_poly_type)
```

As you'll see, the numbers here are low because we didn't actually trace rlang itself, just that some other packages used rlang, giving us limited results.
